Supplementary Materials for cILR: Taxonomic enrichment analysis with isometric log ratios

### 2022-01-26 cbea_revised.tex

\subsection*{Sample level inference}
CBEA provides significance testing for enrichment at the sample level using the null distribution estimation procedure described in \nameref{methods}. Here, we present empirical results for this application of CBEA assessing type I error, power, and classification capacity.

>>>>

\subsection*{Statistical Significance}
\subsubsection*{Inference at the sample level}
CBEA provides significance testing for enrichment at the sample level using the null distribution estimation procedure described in \nameref{methods}. Here, we present empirical results for this application of CBEA assessing type I error, power, and classification capacity.

\begin{figure}[!h]
    \centering
    \includegraphics[width = \textwidth]{figures/data_ss_fdr_new.png}
    \caption{Type I error for sample-level inference with CBEA under different parametric assumptions compared against a Wilcoxon rank-sum test at a nominal $\alpha$ of 0.05. } 
    \label{fig:2}
\end{figure}
